Online Verification of Commutativity

### 2020-07-31 acmPaper/paper.tex
sketch of evaluation

\newcount\draft\draft=1 % set to 0 for submission or publication
\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usepackage{amssymb}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Evaluation}
We compare performance of the following path checking algorithms: (1) naive baseline (2) less naive, two-flip baseline (3) batch baseline (4) algorithm ~\ref{algo_online_polynomial}, and (5) algorithm ~\ref{algo_online_minimal}.
The two aspects we look at are time for response and size of response set (smaller sets -- tighter output results -- would mean less calls to the oracle).
We use randomly generated graphs for benchmarking, and vary their size.
All computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.

The naive baseline performs poorly, taking well over a thousand seconds for even small graphs of 10 nodes.
The batch algorithm brings timing down to seconds. Algorithm ~\ref{algo_online_polynomial} performs only slightly better.
Surprisingly, the optimal set algorithm cuts time cost by several orders of magnitude.
All implementations are sensitive to density, performing better when density is very low or very high.

%TODO add figures

\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds taken for ten nodes, density close to 0.5 \\
    \hline
    Naive baseline & 1,500 \\
    Batch algorithm & 1.4 \\
    algorithm ~\ref{algo_online_polynomial} & 1.2 \\
    algorithm ~\ref{algo_online_minimal} & 0.0006 \\
    \hline
\end{tabular}

>>>>

\newcount\draft\draft=1 % set to 0 for submission or publication
\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usepackage{amssymb}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Evaluation}
We compare performance of the following path checking algorithms: (1) naive baseline (2) less naive, two-flip baseline (3) batch baseline (4) algorithm ~\ref{algo_online_polynomial}, and (5) algorithm ~\ref{algo_online_minimal}.
The two aspects we look at are time for response and size of response set (smaller sets -- tighter output results -- would mean less calls to the oracle).
We use randomly generated graphs for benchmarking, and vary their size.
Given a graph and a new edge, we time how long it takes for an algorithm to return 
All computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.

The naive baseline performs poorly, taking well over a thousand seconds for even small graphs of 10 nodes.
The batch algorithm brings timing down to seconds. Algorithm ~\ref{algo_online_polynomial} performs only slightly better.
Surprisingly, the optimal set algorithm cuts time cost by several orders of magnitude, and runs in milliseconds for small graphs.
All implementations are sensitive to density, performing better when density is very low or very high.

\section{Comparison of algorithm time cost}
The average time taken by each algorithm over the course of 10 runs over randomly generated graphs with 8 nodes and 32 edges is listed in table ~\ref{times}.

%TODO get this data.
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Naive baseline & 1,500 \\
    Two Flip tolerant & 1 \\
    Batch algorithm & 1.4 \\
    algorithm ~\ref{algo_online_polynomial} & 1.2 \\
    algorithm ~\ref{algo_online_minimal} & 0.0006 
    \hline
    \label{times}
\end{tabular}

\section{Scaling of time with input size}

Algorithms scale as expected with time, as seen in figure ~\ref{fig:timeVsSize}. 
Both algorithm ~\ref{algo_online_minimal} and ~\ref{algo_minimal_spanning_set} exhibit graphs that are polynomial in appearance, as does the batch baseline.
\xxx[AK]{Do I need to justify this by doing some kind of fit?}
The naive baseline as well as the two flip tolerant baseline display catastrophic growth that quickly makes computation untenable.

Further, run time is found to relate to the density of edges in the input graph.
We define density to be the ratio of the number of edges in the graph to the total possible number of edges ($|V|^2$, where $|V|$ is the number of nodes).
Generally, time cost is found to be higher at middling densities and lower as density approaches 0 or 1.

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{.2\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfig1}
    \end{subfigure}
    \begin{subfigure}{.2\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfig2}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density}
    \label{fig:timeVsSize}
    %TODO add plots for two flip, naive, batch checker
\end{figure}

\section{Variance}
For all algorithms, there is considerable spread in the time taken for a given graph size, varying with graph structure.
The plots in figure ~\ref{fig:timeVsSize} %TODO replace
depict the situation.
After computation on 10 randomly generated graphs of density 0.5, each outcome is plotted as a point and error bars indicate standard deviation.

%TODO add a figure for each of the checkers.

\section{Size of Output}
Output size is found to be along similar lines to time cost.
Table ~\ref{sizes}, the size analog of table ~\ref{times} summarizes the number of output pairs that the algorithms returned on average over 10 runs, for graphs with 8 nodes and 32 edges.
% TODO get this data.
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Naive baseline & 1,500 \\
    Two Flip tolerant & 1 \\
    Batch algorithm & 1.4 \\
    algorithm ~\ref{algo_online_polynomial} & 1.2 \\
    algorithm ~\ref{algo_online_minimal} & 0.0006
    \hline
    \label{sizes}
\end{tabular}
